Implementing simplified INLA into `aghq`

### 2022-10-12 src/dev_sinla/sinla.Rmd
Normalise the Laplace approximation with trapezoid rule in 1D

#' How many equally spaced points do we want to evaluate the posterior at?
phi_prev_i_grid_length <- 50

df <- opt$par %>%
  t() %>%
  as.data.frame() %>%
  slice(rep(1:n(), each = phi_prev_i_grid_length)) %>%
  mutate(
    phi_prev_i = seq(from = 0.5, to = 3.5, length.out = phi_prev_i_grid_length)
  ) %>%
  rowwise() %>%
  mutate(
    #' Note here: it's crucial that the arguments are in the right order!
    logpost = -obj$fn(c(beta_prev, phi_prev_i, log_sigma_phi_prev))
  )

@@

```{r}
df <- df %>%
  mutate(
    logpost_mean = colMeans(select(., logpost)),
    logpost_adj = logpost - logpost_mean,
    post = exp(logpost_adj)
  )

plot3 <- plot2 +
  geom_line(data = df, aes(x = phi_prev_i, y = post), col = cbpalette[5], size = 1)

#' Need to normalise this!
plot3
```

>>>>

#' How many equally spaced points do we want to evaluate the posterior at?
spacing <- 0.05
x_grid <- seq(from = 0.5, to = 3.5, by = spacing)
x_grid_length <- length(x_grid)

df <- opt$par %>%
  t() %>%
  as.data.frame() %>%
  slice(rep(1:n(), each = x_grid_length)) %>%
  mutate(
    phi_prev_i = x_grid
  ) %>%
  rowwise() %>%
  mutate(
    #' Note here: it's crucial that the arguments are in the right order!
    logpost = -obj$fn(c(beta_prev, phi_prev_i, log_sigma_phi_prev))
  )

@@

```{r}
safe_exp <- function(x) exp(x - max(x))

trapezoid_rule <- function(x, spacing) {
  0.5 * spacing * (2 * sum(x) - x[1] - x[2])
}

df$post <- safe_exp(df$logpost)
df$post_norm = df$post / trapezoid_rule(df$post, spacing)

plot3 <- plot2 +
  geom_line(data = df, aes(x = phi_prev_i, y = post_norm), col = cbpalette[5], size = 1)

plot3
```

So perhaps it's barely better than the Gaussian, but not really getting the real problem here.
Hypothesis would be that it's because we're doing empirical Bayes, and with more than one hyperparameter grid point we would do better.
